Interpreting Random Forest Predictions for Firearm Identification Using LIME

### 2018-10-31 paper/paper.Rmd
updates to app

  # Apply the explain function from the lime package (with a seed set)
  set.seed(84902)
  hamby224_explain <- lime::explain(hamby224_test %>% select(rf_features), 
                                    hamby224_lime,
                                    labels = "TRUE",
                                    n_features = 3)

@@

Some plots to tryout working with the new explanations...

>>>>

  # Apply the explain function from the lime package (with a seed set)
  set.seed(84902)
  hamby224_explain <- lime::explain(hamby224_test %>% select(rf_features), 
                                    hamby224_lime,
                                    labels = "FALSE",
                                    n_features = 3)

@@

Thoughts on the visualizations:

- It would be interesting to see the "magnitude" associated with a variable for a prediction, but
  this would require obtaining the scaled values of the perturbations.
- This seems much more meaningful to me than just the model coefficient associated with the variable.
- The current version shows which variables in the model have the largest coefficients.
- However, the importance of the variable might change depending on the observed value associated
  with the prediction of interest.
